\chapter{References}

Gardner-Stephen, P., Challans, R., Lakeman, J., Bettison, A., Lieser, P., Steinmetz, R., Alvarez, F. and Lloyd, M. (2017). Productizing humanitarian telecommunications research: A case study of the Serval Mesh Extender. 2017 IEEE Global Humanitarian Technology Conference (GHTC).

\hfill \break
Gardner-Stephen, P., Farouque, S., Lloyd, M., Bate, A. and Cullen, A. (2017). Piloting the serval mesh and serval mesh extender 2.0 in Vanuatu: Preliminary results. 2017 IEEE Global Humanitarian Technology Conference (GHTC).

\hfill \break
Gardner-Stephen, P. (2018). Building an indoor test network and testing LBARD bug fixes. [online] Servalpaul.blogspot.com. Available at: \url{http://servalpaul.blogspot.com/2018/04/building-indoor-test-network-and.html} [Accessed 30 Jun. 2018].

\hfill \break
Gardner-Stephen, P. (2018). Fixing bugs and structure of LBARD. [online] Servalpaul.blogspot.com. Available at: 
\url{http://servalpaul.blogspot.com/2018/04/fixing-bugs-and-structure-of-lbard.html} [Accessed 30 Jun. 2018].

\hfill \break
Brodkin, J. (2017). Tropical Storm Harvey takes out 911 centers, cell towers, and cable networks. [online]
Ars Technica. Available at: \url{https://arstechnica.com/information-technology/2017/08/tropical-storm-harvey-
takes-out-911-centers-cell-towers-and-cable-networks/} [Accessed 15 Mar. 2018].

\hfill \break
Encyclopedia Britannica. (2017). Haiti earthquake of 2010 $|$ Effects, Damage, Map, \& Facts. [online]
Available at: \url{https://www.britannica.com/event/Haiti-earthquake-of-2010} [Accessed 15 Mar. 2018].


\hfill \break
London.gov.uk. (2007). [online] Available at:
\url{https://www.london.gov.uk/sites/default/files/gla_migrate_files_destination/archives/assembly-reports-
7july-follow-up-report.pdf} [Accessed 15 Mar. 2018].

\hfill \break
Telstra.com.au. (2018). Telstra - Our Coverage. [online] Available at: \url{https://www.telstra.com.au/coverage-
networks/our-coverage#disclaimer} [Accessed 15 Mar. 2018].


\hfill \break
Gardner-Stephen, P., Challans, R., Lakeman, J., Bettison, A., Gardner-Stephen, D. and Lloyd, M. (2013). The serval
mesh: A platform for resilient communications in disaster \&amp; crisis. 2013 IEEE Global Humanitarian Technology
Conference (GHTC).
